ISF Grant

### 2017-10-03 article.tex
Model 2

\begin{abstract}
	a
\end{abstract}

\section{Introduction}

Traditional computer architectures containing both a volatile main memory alongside a non-volatile secondary storage, have led to a separation of program state into operational data stored using in-memory data structures, and recovery data stored using sequential on-disk structures such as transaction logs. A system-wide failure, such as a power outage, cause a full lost of the in-memory data structures, which must be reconstructed entirely from the recovery data, making the software system temporarily unavailable. As a result, the design of in-memory data structures emphasise disposable constructs optimized for parallelism, in contrast to the structures that hold recovery data, which cannot be discarded upon a failure and which benefit less from parallelism since their performance is limited by the secondary storage.

Current industry projections indicate that non-volatile main memory (NVRAM) will become commonplace over the next few years. While the availability of NVRAM suggests the possibility of keeping persistent data in main memory (not just in the file system), the fact that recent updates to registers and cache may be lost during a power failure means that the data in main memory, if not carefully managed, may not be consistent at recovery time.
Traditional log-based recovery techniques, although can be applied correctly in such systems, fail to take full advantage of the parallelism enabled by allowing processing cores to access recovery data directly using memory operations rather than slow block transfers from secondary storage. As a result, harnessing the performance benefits of NVRAM-based platforms requires a careful rethinking of recovery mechanisms.

The study of shared data structures and concurrent programming dates back over a half century ago. 1965 Dijkstra's pioneering work presented the concept of concurrent programming [*], followed by a series of seminal papers on inter-process communication, wait-free synchronization, and linearizability [*].
Recent research has paid close attention to asynchronous models, in which there is no bound on the amount of time a process takes to transition to its next step, or to complete a memory operation. This assumption captures the behaviour of most modern memory hierarchies, where different media (e.g., L1 cache vs. L2 cache vs. main memory) incur vastly different and often unpredictable access latencies, as well as the effect of the operating system (e.g., via preemption and interrupts) on the liveness of processes. In addition, asynchrony is also related to reliability in a precise way: algorithms that provide non-blocking progress properties (e.g., lock-freedom and wait-freedom) in an asynchronous environment with reliable processes continue to provide the same progress properties if crash failures are introduced. Informally speaking, this property holds because a process that crashes permanently at an arbitrary point in the execution of its algorithm is indistinguishable to the other processes from one that is merely very slow.

@@

RR-linearizability does not specify the progress property required from the implementation. One can use a recoverable mutual exclusion lock at the recovery code in order to sequentially let the processes complete their pending operations. Obviously, this solution is not desired when the operation implementation we are recovering is wait-free. In this case, we would like the recovery code to be wait-free as well, meaning that a process finish it in a finite number of its own steps in the absence of failure. One more point that requires our attention is the possibility of a failure along the recovery code. Would it be realistic to assume that such a scenario will not happen? Of course, a recovery code that can suffer itself failures is better. However, this is not well defined. If we allow each failure to run new and different recovery code, we can use a nesting technique in a way which increase the running time with each failure. A better approach will be such that in the case of failure inside of a recovery code, restarting the recovery code, from the beginning any other point, is enough. In such case, if the recovery code is wait-free in the absence of a failure, we can guarantee that no matter how many failures the process experienced, once given enough time with no failure, it will finish the recovery code (and therefore the pending operation) in a wait-free manner.

>>>>

@@

RR-linearizability does not specify the progress property required from the implementation. One can use a recoverable mutual exclusion lock at the recovery code in order to sequentially let the processes complete their pending operations. Obviously, this solution is not desired when the operation implementation we are recovering is wait-free. In this case, we would like the recovery code to be wait-free as well, meaning that a process finish it in a finite number of its own steps in the absence of failure. One more point that requires our attention is the possibility of a failure along the recovery code. Will it be realistic to assume that such a scenario will not happen? Of course, a recovery code that can suffer itself failures is better. However, this is not well defined. If we allow each failure to run new and different recovery code, we can use a nesting technique in a way which increase the running time with each failure. This may also requires infinite memory and code. A better approach will be such that in the case of failure inside of a recovery code, restarting the recovery code from some point is enough. In such case, if the recovery code is wait-free in the absence of a failure, we can guarantee that no matter how many failures the process experienced, once given enough time with no failure, it will finish the recovery code (and therefore the pending operation) in a wait-free manner.

The standard abstract model is consider in this work. The system consist of set of asynchronous unreliable processes $P=\{p_1,\ldots,p_n\}$ that communicate by applying operations on shared \emph{base objects} that support atomic operations such as reads, writes, and read-modify-write primitives.

We assume that a once a process crash, the system knows at which line of the code the fail happened. However, there is no indication whether the instruction at that line tool affect before the crash. Upon recovering, the controller moves the process to a recovery code according to the line where the crash occur. By running this code, the process is aware that a crash happened, as well as at what line of the code was it.
